### 2024-03-15 sections/2homology.tex
cref -> Cref

\begin{remark}
    Because of \cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the weakly constructible bundle $f$.
\end{remark}

>>>>

\begin{remark}
    Because of \Cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the weakly constructible bundle $f$.
\end{remark}

### 2024-03-15 sections/3algebras.tex
cref -> Cref

Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is. For prefactorization algebras, the answer comes by definition, but this is not the case for factorization algebras. In the case of stratified manifolds, we will show that the $\infty$-operad that governs locally constant factorization algebras can be taken to be $\disk_{/M}$, and the one that governs ordinary factorization algebras can be taken to be $\disk[r]_{/M}$. This result is immensely helpful in relating factorization algebras to results in the area of disk algebras. We will see one such example in \cref{ch:gluing_disk_alg}.

@@

    We first observe that, by definition, the $\infty$-operad $\opens(M) := \mfld[r]_{/M}$. There are clear functors of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \xhookrightarrow{\ \ \ } \mfld_{/M} \xleftarrow{\ \ \ } \mfld[r]_{/M}.
    \end{equation}
    %
    At the level of algebras over them, they give rise to the commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\disk_{/M}} (\catC) \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l] \arrow[r] & \mathsf{Fun}(\opens(M), \catC),
        \end{tikzcd}
    \end{equation}
    %
    where the vertical arrows are forgetful functors. Factorization homology as a left Kan extension gives one the adjoints indicated below
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC).
        \end{tikzcd}
    \end{equation}
    %
    A result found in \cite[thm.1.2.5]{aft_localstrut} (where they use slightly different notation and call locally constant sheaves constructible) gives us the equivalence
    %
    \begin{equation}
        \csheaves[W](\mfld_{/M}, \catC) \simeq \csheaves[W, lc](\mfld[r]_{/M}, \catC) =: \csheaves[W, lc]_M(\catC),
    \end{equation}
    %
    which at the level of underlying functors, is exactly the restriction along the functor $\opens(M) \xrightarrow{} \mfld_{/M}$, so that we can append this to our commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] \arrow[dr, dashed] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC) \\
            & \csheaves[W](\mfld_{/M}, \catC) \arrow[r, "\simeq"] \arrow[u] & \csheaves[W, lc]_M(\catC) \arrow[u].
        \end{tikzcd}
    \end{equation}
    %
    If we can find the dashed functor which makes the diagram commute, as indicated above, we would be done with the construction. This amounts to showing that the left Kan extension $\int F$ of a functor $F \in \mathsf{Fun}(\disk_{/M}, \catC)$ along $\disk_{/M} \xhookrightarrow{} \mfld_{/M}$ is automatically a Weiss cosheaf. By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding. Here we notice that for the Weiss property to even make sense, we are implicitly using \cref{lem:double_slice}

    Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
    %
    \begin{equation}\label{eq:pointwiseKan}
        \int_e F \simeq \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
    \end{equation}
    %
    so what we need to show is that this colimit is equivalent to the colimit
    %
    \begin{equation}\label{eq:cosheaf_colim_relative}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \rightarrow \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    for each covering sieve $\mathscr{U}$. Since we aren't actually trying to get the value of these colimits we can rewrite \cref{eq:pointwiseKan} into the idiosyncratic form
    %
    \begin{equation}\label{eq:idiosync_form}
        \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    which is easier to compare to \cref{eq:cosheaf_colim_relative}. Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalences of \cref{lem:double_slice} we can rewrite \cref{eq:idiosync_form} further into
    %
    \begin{align}
        \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \\ \simeq \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC).
    \end{align}
    %
    Denoting the functor $\mfld[r]_{/N} \simeq (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC$ by $K_F$ and comparing with \cref{eq:cosheaf_colim_relative} we need to show
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C) \simeq \mathsf{colim} (\disk[r]_{/N} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C),
    \end{equation}
    %
    but this already follows from part 2 of the proof of \cite[prop.2.22]{af_primer}, and is equivalent to the statement that the functor
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} \disk_{/N},
    \end{equation}
    %
    is final.
\end{proof}

@@

From the proof of \cref{prop:fh_disk_to_lcfa} it is easy to see that we can make a similar statement for ordinary factorization algebras too:

@@

\begin{proof}
    To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later. Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding equivalences of prefactorization algebras, namely a family of equivalences
    %
    \begin{equation}
        \int_U F| \xrightarrow[\simeq]{\ \ \phi (U) \ \ } F(U),
    \end{equation}
    %
    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which preserve the multiplicative structure (see \cref{cd:fa_morphisms}). Since $F$ is a locally constant factorization algebra the functor
    %
    \begin{equation}
        \lcfa_M (\catC) \xrightarrow{} \csheaves[W, lc](\mfld[r]_{/M}, \catC) \simeq \csheaves[W](\mfld_{/M}, \catC) \xrightarrow{} \mathsf{Fun}(\mfld_{/M}, \catC),
    \end{equation}
    %
    which we omit in the notation, allows us to consider $F$ as a functor from $\mfld_{/M}$. Furthermore, since $\disk[r]_{/U}$ is a Weiss sieve we can write
    %
    \begin{align}
        F(U) &\simeq \mathsf{colim} (\disk[r]_{/U} \xrightarrow{} \disk[r]_{/M} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{F} \catC).
    \end{align}
    %
    By consulting the commutative diagram
    % 
    \begin{equation}
        \begin{tikzcd}
            \disk[r]_{/U} \arrow[d] \arrow[r] & \disk_{/U} \arrow[d] & \\
            \disk[r]_{/M} \arrow[d] \arrow[r] & \disk_{/M} \arrow[d] \arrow[r, "F|"] & \catC, \\
            \mfld[r]_{/M} \arrow[r] & \mfld_{/M} \arrow[ru, "F"'] &  
        \end{tikzcd}
    \end{equation}
    %
    and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
    %
    \begin{equation}
        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) =: \int_U F|.
    \end{equation}
    %
    To preserve the multiplicative structure, these equivalences have to be natural, and there also has to be a commutative diagram
    %
    \begin{equation}\label{eq:mult_strut_comm_square}
        \begin{tikzcd}
            \otimes_i \int_{U_i} F| \arrow[r, "\simeq"] \arrow[d, "\otimes_i \phi (U_i)"', "\simeq"] & \int_{\sqcup_i U_i} F| \arrow[d, "\phi (\sqcup_i U_i)", "\simeq"']\\
            \otimes_i F (U_i) \arrow[r, "\simeq"] & F (\sqcup_i U_i),
        \end{tikzcd}
    \end{equation}
    %
    for each collection of disjoint open sets $\{U_i\}$. Naturality is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$. On the other hand, the existence of the commutative diagram is guaranteed by the equivalence
    %
    \begin{equation}
        \disk[r]_{/\sqcup_i U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_i \disk[r]_{/U_i}.
    \end{equation}

@@

\begin{remark}
    A version of \cref{thm:disk_alg=lcfa} was proven as \cite[thm.6]{gtz2014} in the case of smooth manifolds. The proof there, however, made crucial use of choosing a Riemannian metric on the manifold and constructing geodesically convex neighborhoods. This technique is, at least presently, not extendable to the stratified case, but our proof above subverts the need for it. 
\end{remark}

@@

\begin{proof}
    We follow the proof of \cite[cor.2.33]{aft_fhstrat}. Using \cref{rem:disk_b=disk_bsc}, the forgetful functor from the slice $\infty$-operad, which is a map of $\infty$-operads, is what will provide the equivalence
    %
    \begin{equation}
        \disk_{/M} \simeq \disk(\bstr_M)_{/M} \xrightarrow{\ \ \ \ } \disk(\bstr_M).
    \end{equation}
    %
    This functor is an equivalence on maximal $\infty$-subgroupoids because for any $V \in \disk(\bstr_M)$ the space of morphisms to $M$ is contractible, so, up to equivalence it is unique. %To check that it is fully faithful we need to show that the induced maps
    %
    %\begin{equation}
    %    \mathsf{Hom}_{\disk(\bstr)_{/U}} (V \xhookrightarrow{} U, V' \xhookrightarrow{} U) \xrightarrow{\ \ \ \ } \mathsf{Hom}_{\disk(\bstr)} (V, V')
    %\end{equation}
    %
    %are equivalences. Giving a functor $\disk (\bstr) \xrightarrow{} \disk (\bstr)_{/U}$ is the same as giving a functor
    %
    %\begin{equation}
    %    \disk (\bstr) ^{\vartriangleright} \xrightarrow{} \disk (\bstr)_{/U},
    %\end{equation}
    %
    %which sends the cone point to $U$ (see e.g. \cite[prop.3.2]{joyal}).
    Full faithfulness is provided by the fact that the functor on the active $\infty$-subcategories $\disk_{/M} \xrightarrow{} \disk(\bstr_M)$ is a right fibration. 
\end{proof}

@@

The results of \cref{thm:disk_alg=lcfa} and \cref{cor:disk_alg=falg} can also be seen as lowering the amount of data that is necessary to say that we have defined a factorization algebra on a stratified manifold. There is a similar, but slightly weaker result by \cite{cg2016}, which nonetheless works for all Hausdorff topological spaces. We recount this result here for comparison.

@@

\begin{remark}
    The proof of \cref{thm:fa_from_basis} can be found in \cite[ch.7.2]{cg2016}, and we will not reproduce it here. The target category there is the category of chain complexes, but it holds more generally in $\catC$ by considering simplicial objects and their geometric realizations (which exist by the colimit assumption on $\catC$) instead.

    As mentioned, in the stratified manifold case, this is an easy corollary of the proof of \cref{prop:fh_disk_to_lcfa}, where we show that taking all disks as the Weiss cover of choice reproduces the result that we would have gotten with any other Weiss cover. It is important to point out though that disks are not necessarily closed under intersections, which means that we don't have the opposite implication, and the methods to prove \cref{prop:fh_disk_to_lcfa} are necessary.
\end{remark}

@@

\begin{corollary}\label{cor:pushforward_for_lc}
    Let $f: M \xrightarrow{} N$ be a constructible bundle of stratified manifolds. Then the pushforward functor for factorization homology of \cref{thm:fh_pushforward} serves as a pushforward
    %
    \begin{equation}
        f_*: \lcfa_M \xrightarrow{\quad} \lcfa_N,
    \end{equation}
    %
    by using \cref{thm:disk_alg=lcfa}.
\end{corollary}

@@

\begin{lemma}\label{lem:ff_functor_to_refinement}
    Let $u: X \rightarrow \hat{X}$ be the morphism of \cref{ex:forget_strat} that forgets the stratification.
    The functor $u_*: \lcfa_{X} (\catC) \rightarrow \lcfa_{\hat{X}} (\catC)$ has a fully faithful left adjoint.
\end{lemma}

@@

\begin{remark}
    The conditions we imposed on $\catC$ allowed us, in \cref{rem:sym_mon_inheritance}, to inherit a symmetric monoidal structure on the $\infty$-categories of factorization algebras of all varieties. It also allowed us to inherit the existence of colimits. This is the reason why the above can even be stated.
\end{remark}

@@

    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using \cref{thm:fa_from_basis}. However, we'll focus on manifolds, in which case, the construction from above immediately works since we now have to do it for $\disk[r]_{/X}$ instead of $\mfld[r]_{/X}$. The only things to mention is that products of disks are again disks \cite[cor.3.4.9]{aft_localstrut}.
\end{proof}

@@

\begin{remark}
    The above proposition also appears as \cite[prop.18]{ginot2015}. The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$. Using \cref{thm:disk_alg=lcfa}, the statement is implied by the fact that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
    \end{equation}
    %
    with the tensor product of $\infty$-opeards. Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}.
\end{remark}

\begin{proof}
    The proof of existence of the functor goes along the same lines as the proof of \cref{prop:exp_of_products} because of \cref{thm:disk_alg=lcfa}. The thing to take into account is that the projection maps are both, trivially, constructible bundles so by \cref{cor:pushforward_for_lc}, pushing forward by them yields locally constant factorization algebras again. This combined with the fact that for any $\infty$-operads $\mathscr{O}$, $\mathscr{O}'$ and $\mathscr{C}$ we have an equivalence
    %
    \begin{equation}
        \alg{\mathscr{O}} (\alg{\mathscr{O}'} (\catC)) \simeq \alg{\mathscr{O}'} (\alg{\mathscr{O}} (\catC))
    \end{equation}
    %
    allows us to conclude that the functor lands in locally constant factorization algebras
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{X \times Y}(\catC) \xrightarrow{\ \ \ \ } \lcfa_{X}(\lcfa_{Y}(\catC)).
    \end{equation}

>>>>

Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is. For prefactorization algebras, the answer comes by definition, but this is not the case for factorization algebras. In the case of stratified manifolds, we will show that the $\infty$-operad that governs locally constant factorization algebras can be taken to be $\disk_{/M}$, and the one that governs ordinary factorization algebras can be taken to be $\disk[r]_{/M}$. This result is immensely helpful in relating factorization algebras to results in the area of disk algebras. We will see one such example in \Cref{ch:gluing_disk_alg}.

@@

    We first observe that, by definition, the $\infty$-operad $\opens(M) := \mfld[r]_{/M}$. There are clear functors of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \xhookrightarrow{\ \ \ } \mfld_{/M} \xleftarrow{\ \ \ } \mfld[r]_{/M}.
    \end{equation}
    %
    At the level of algebras over them, they give rise to the commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\disk_{/M}} (\catC) \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l] \arrow[r] & \mathsf{Fun}(\opens(M), \catC),
        \end{tikzcd}
    \end{equation}
    %
    where the vertical arrows are forgetful functors. Factorization homology as a left Kan extension gives one the adjoints indicated below
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC).
        \end{tikzcd}
    \end{equation}
    %
    A result found in \cite[thm.1.2.5]{aft_localstrut} (where they use slightly different notation and call locally constant sheaves constructible) gives us the equivalence
    %
    \begin{equation}
        \csheaves[W](\mfld_{/M}, \catC) \simeq \csheaves[W, lc](\mfld[r]_{/M}, \catC) =: \csheaves[W, lc]_M(\catC),
    \end{equation}
    %
    which at the level of underlying functors, is exactly the restriction along the functor $\opens(M) \xrightarrow{} \mfld_{/M}$, so that we can append this to our commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] \arrow[dr, dashed] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC) \\
            & \csheaves[W](\mfld_{/M}, \catC) \arrow[r, "\simeq"] \arrow[u] & \csheaves[W, lc]_M(\catC) \arrow[u].
        \end{tikzcd}
    \end{equation}
    %
    If we can find the dashed functor which makes the diagram commute, as indicated above, we would be done with the construction. This amounts to showing that the left Kan extension $\int F$ of a functor $F \in \mathsf{Fun}(\disk_{/M}, \catC)$ along $\disk_{/M} \xhookrightarrow{} \mfld_{/M}$ is automatically a Weiss cosheaf. By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding. Here we notice that for the Weiss property to even make sense, we are implicitly using \Cref{lem:double_slice}

    Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
    %
    \begin{equation}\label{eq:pointwiseKan}
        \int_e F \simeq \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
    \end{equation}
    %
    so what we need to show is that this colimit is equivalent to the colimit
    %
    \begin{equation}\label{eq:cosheaf_colim_relative}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \rightarrow \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    for each covering sieve $\mathscr{U}$. Since we aren't actually trying to get the value of these colimits we can rewrite \Cref{eq:pointwiseKan} into the idiosyncratic form
    %
    \begin{equation}\label{eq:idiosync_form}
        \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    which is easier to compare to \Cref{eq:cosheaf_colim_relative}. Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalences of \Cref{lem:double_slice} we can rewrite \Cref{eq:idiosync_form} further into
    %
    \begin{align}
        \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \\ \simeq \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC).
    \end{align}
    %
    Denoting the functor $\mfld[r]_{/N} \simeq (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC$ by $K_F$ and comparing with \Cref{eq:cosheaf_colim_relative} we need to show
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C) \simeq \mathsf{colim} (\disk[r]_{/N} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C),
    \end{equation}
    %
    but this already follows from part 2 of the proof of \cite[prop.2.22]{af_primer}, and is equivalent to the statement that the functor
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} \disk_{/N},
    \end{equation}
    %
    is final.
\end{proof}

@@

From the proof of \Cref{prop:fh_disk_to_lcfa} it is easy to see that we can make a similar statement for ordinary factorization algebras too:

@@

\begin{proof}
    To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later. Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding equivalences of prefactorization algebras, namely a family of equivalences
    %
    \begin{equation}
        \int_U F| \xrightarrow[\simeq]{\ \ \phi (U) \ \ } F(U),
    \end{equation}
    %
    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which preserve the multiplicative structure (see \Cref{cd:fa_morphisms}). Since $F$ is a locally constant factorization algebra the functor
    %
    \begin{equation}
        \lcfa_M (\catC) \xrightarrow{} \csheaves[W, lc](\mfld[r]_{/M}, \catC) \simeq \csheaves[W](\mfld_{/M}, \catC) \xrightarrow{} \mathsf{Fun}(\mfld_{/M}, \catC),
    \end{equation}
    %
    which we omit in the notation, allows us to consider $F$ as a functor from $\mfld_{/M}$. Furthermore, since $\disk[r]_{/U}$ is a Weiss sieve we can write
    %
    \begin{align}
        F(U) &\simeq \mathsf{colim} (\disk[r]_{/U} \xrightarrow{} \disk[r]_{/M} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{F} \catC).
    \end{align}
    %
    By consulting the commutative diagram
    % 
    \begin{equation}
        \begin{tikzcd}
            \disk[r]_{/U} \arrow[d] \arrow[r] & \disk_{/U} \arrow[d] & \\
            \disk[r]_{/M} \arrow[d] \arrow[r] & \disk_{/M} \arrow[d] \arrow[r, "F|"] & \catC, \\
            \mfld[r]_{/M} \arrow[r] & \mfld_{/M} \arrow[ru, "F"'] &  
        \end{tikzcd}
    \end{equation}
    %
    and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
    %
    \begin{equation}
        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) =: \int_U F|.
    \end{equation}
    %
    To preserve the multiplicative structure, these equivalences have to be natural, and there also has to be a commutative diagram
    %
    \begin{equation}\label{eq:mult_strut_comm_square}
        \begin{tikzcd}
            \otimes_i \int_{U_i} F| \arrow[r, "\simeq"] \arrow[d, "\otimes_i \phi (U_i)"', "\simeq"] & \int_{\sqcup_i U_i} F| \arrow[d, "\phi (\sqcup_i U_i)", "\simeq"']\\
            \otimes_i F (U_i) \arrow[r, "\simeq"] & F (\sqcup_i U_i),
        \end{tikzcd}
    \end{equation}
    %
    for each collection of disjoint open sets $\{U_i\}$. Naturality is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$. On the other hand, the existence of the commutative diagram is guaranteed by the equivalence
    %
    \begin{equation}
        \disk[r]_{/\sqcup_i U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_i \disk[r]_{/U_i}.
    \end{equation}

@@

\begin{remark}
    A version of \Cref{thm:disk_alg=lcfa} was proven as \cite[thm.6]{gtz2014} in the case of smooth manifolds. The proof there, however, made crucial use of choosing a Riemannian metric on the manifold and constructing geodesically convex neighborhoods. This technique is, at least presently, not extendable to the stratified case, but our proof above subverts the need for it. 
\end{remark}

@@

\begin{proof}
    We follow the proof of \cite[cor.2.33]{aft_fhstrat}. Using \Cref{rem:disk_b=disk_bsc}, the forgetful functor from the slice $\infty$-operad, which is a map of $\infty$-operads, is what will provide the equivalence
    %
    \begin{equation}
        \disk_{/M} \simeq \disk(\bstr_M)_{/M} \xrightarrow{\ \ \ \ } \disk(\bstr_M).
    \end{equation}
    %
    This functor is an equivalence on maximal $\infty$-subgroupoids because for any $V \in \disk(\bstr_M)$ the space of morphisms to $M$ is contractible, so, up to equivalence it is unique. %To check that it is fully faithful we need to show that the induced maps
    %
    %\begin{equation}
    %    \mathsf{Hom}_{\disk(\bstr)_{/U}} (V \xhookrightarrow{} U, V' \xhookrightarrow{} U) \xrightarrow{\ \ \ \ } \mathsf{Hom}_{\disk(\bstr)} (V, V')
    %\end{equation}
    %
    %are equivalences. Giving a functor $\disk (\bstr) \xrightarrow{} \disk (\bstr)_{/U}$ is the same as giving a functor
    %
    %\begin{equation}
    %    \disk (\bstr) ^{\vartriangleright} \xrightarrow{} \disk (\bstr)_{/U},
    %\end{equation}
    %
    %which sends the cone point to $U$ (see e.g. \cite[prop.3.2]{joyal}).
    Full faithfulness is provided by the fact that the functor on the active $\infty$-subcategories $\disk_{/M} \xrightarrow{} \disk(\bstr_M)$ is a right fibration. 
\end{proof}

@@

The results of \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} can also be seen as lowering the amount of data that is necessary to say that we have defined a factorization algebra on a stratified manifold. There is a similar, but slightly weaker result by \cite{cg2016}, which nonetheless works for all Hausdorff topological spaces. We recount this result here for comparison.

@@

\begin{remark}
    The proof of \Cref{thm:fa_from_basis} can be found in \cite[ch.7.2]{cg2016}, and we will not reproduce it here. The target category there is the category of chain complexes, but it holds more generally in $\catC$ by considering simplicial objects and their geometric realizations (which exist by the colimit assumption on $\catC$) instead.

    As mentioned, in the stratified manifold case, this is an easy corollary of the proof of \Cref{prop:fh_disk_to_lcfa}, where we show that taking all disks as the Weiss cover of choice reproduces the result that we would have gotten with any other Weiss cover. It is important to point out though that disks are not necessarily closed under intersections, which means that we don't have the opposite implication, and the methods to prove \Cref{prop:fh_disk_to_lcfa} are necessary.
\end{remark}

@@

\begin{corollary}\label{cor:pushforward_for_lc}
    Let $f: M \xrightarrow{} N$ be a constructible bundle of stratified manifolds. Then the pushforward functor for factorization homology of \Cref{thm:fh_pushforward} serves as a pushforward
    %
    \begin{equation}
        f_*: \lcfa_M \xrightarrow{\quad} \lcfa_N,
    \end{equation}
    %
    by using \Cref{thm:disk_alg=lcfa}.
\end{corollary}

@@

\begin{lemma}\label{lem:ff_functor_to_refinement}
    Let $u: X \rightarrow \hat{X}$ be the morphism of \Cref{ex:forget_strat} that forgets the stratification.
    The functor $u_*: \lcfa_{X} (\catC) \rightarrow \lcfa_{\hat{X}} (\catC)$ has a fully faithful left adjoint.
\end{lemma}

@@

\begin{remark}
    The conditions we imposed on $\catC$ allowed us, in \Cref{rem:sym_mon_inheritance}, to inherit a symmetric monoidal structure on the $\infty$-categories of factorization algebras of all varieties. It also allowed us to inherit the existence of colimits. This is the reason why the above can even be stated.
\end{remark}

@@

    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using \Cref{thm:fa_from_basis}. However, we'll focus on manifolds, in which case, the construction from above immediately works since we now have to do it for $\disk[r]_{/X}$ instead of $\mfld[r]_{/X}$. The only things to mention is that products of disks are again disks \cite[cor.3.4.9]{aft_localstrut}.
\end{proof}

@@

\begin{remark}
    The above proposition also appears as \cite[prop.18]{ginot2015}. The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$. Using \Cref{thm:disk_alg=lcfa}, the statement is implied by the fact that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
    \end{equation}
    %
    with the tensor product of $\infty$-opeards. Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}.
\end{remark}

\begin{proof}
    The proof of existence of the functor goes along the same lines as the proof of \Cref{prop:exp_of_products} because of \Cref{thm:disk_alg=lcfa}. The thing to take into account is that the projection maps are both, trivially, constructible bundles so by \Cref{cor:pushforward_for_lc}, pushing forward by them yields locally constant factorization algebras again. This combined with the fact that for any $\infty$-operads $\mathscr{O}$, $\mathscr{O}'$ and $\mathscr{C}$ we have an equivalence
    %
    \begin{equation}
        \alg{\mathscr{O}} (\alg{\mathscr{O}'} (\catC)) \simeq \alg{\mathscr{O}'} (\alg{\mathscr{O}} (\catC))
    \end{equation}
    %
    allows us to conclude that the functor lands in locally constant factorization algebras
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{X \times Y}(\catC) \xrightarrow{\ \ \ \ } \lcfa_{X}(\lcfa_{Y}(\catC)).
    \end{equation}
